### 2014-09-15 PrivacyProtection-2014-09-09.tex
Further restructuring and cleanup.

\chapter{Privacy Protection}

@@

%\includegraphics{../diagrams/png/implicit-privacy-violation-matrix.png}
\input{./figures/Implicit-Privacy-Violation-Matrix}
\input{./figures/ThreatTable}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Privacy of The Person:} reflexive violation
\item
  \textbf{Privacy of Behaviour and Action:} none
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Some psychological diseases
  (e.g.~depression) have physiological impact. Such physiological
  patterns could be detected.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} none
\end{itemize}

\subparagraph{Privacy of Behaviour and Action}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Privacy of The Person:} Religious practices may include body
  modifications (e.g.~circumcision).
\item
  \textbf{Privacy of Behaviour and Action:} reflexive violation
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Social activities in
  general depend on a certain intellectual attitude. Such an actvity is
  the expressions of such an attitude.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} Recording religious, politcal or
  sexual activities can reveal association with churches, political
  parties or sexual partners.
\end{itemize}

\subparagraph{Privacy of Communication}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Privacy of The Person:} Communication about body
  characteristics.
\item
  \textbf{Privacy of Behaviour and Action:} Communicatio about social
  activities.
\item
  \textbf{Privacy of Communication:} reflexive violation
\item
  \textbf{Privacy of Data and Image:} Communication containing one's
  passwords or other sensitive data.
\item
  \textbf{Privacy of Thoughts and Feelings:} Communication of thoughts
  and feelings, e.g.~wiretapping a flirt or a catholic confession
  ritual.
\item
  \textbf{Privacy of Location and Space:} Interception of face-to-face
  communication is only possible if one's location and space is violated
  (wiretapping).
\item
  \textbf{Privacy of Association:} Communication about one's
  associations (family members, churches, etc.).
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Privacy of The Person:} Images or stored biometric information
  reveal one's physical characteristics.
\item
  \textbf{Privacy of Behaviour and Action:} Images or diaries can reveal
  one's social activities.
\item
  \textbf{Privacy of Communication:} Modern communication systems
  usually contain some sort of archive function, e.g.~E-mail clients do
  not automatically delete messages. Such messages are data and reveal
  one's communication.
\item
  \textbf{Privacy of Data and Image:} reflexive violation
\item
  \textbf{Privacy of Thoughts and Feelings:} Images can show one's
  emotional state.
\item
  \textbf{Privacy of Location and Space:} Images can reveal one's
  location, e.g.~making a picture in front of the Eifel Tower.
\item
  \textbf{Privacy of Association:} E-mail data can also reveal
  association.
\end{itemize}

\subparagraph{Privacy of Thoughts and Feelings}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Privacy of The Person:} Thoughts and feelings can reveal
  medical conditions.
\item
  \textbf{Privacy of Behaviour and Action:} Thoughts and feelings can
  reveal a certain attitudes which create a foundation for certain
  social activities.
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} reflexive violation
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} Thoughts and feelings can reveal
  individual association, e.g amorous feelings for a certain person.
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Privacy of The Person:} Frequently visited doctors can reveal
  certain medical conditions, if such doctors are known specialsts. In
  general it could imply ill-being.
\item
  \textbf{Privacy of Behaviour and Action:} Frequently visited places in
  general can reveal association and hence implies social activities.
\item
  \textbf{Privacy of Communication:} If one's location is knwon, it is
  possible to intercept (wiretap) one's communication. This also may
  violate the right to private spaces.
\item
  \textbf{Privacy of Data and Image:} If one's location is known, it is
  possible shoot pictures. This violates the right to one's image
  (\emph{``Recht am eigenen Bild''}).
\item
  \textbf{Privacy of Thoughts and Feelings:} Frequently visited persons
  may imply certain thoughts and feelings, e.g.~having a mistress.
\item
  \textbf{Privacy of Location and Space:} reflexive violation
\item
  \textbf{Privacy of Association:} Frequently visted places can reveal
  associations simply by searching in maps or yellow-pages.
\end{itemize}

\subparagraph{Privacy of Association}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Privacy of The Person:} Association with tatoo artists could
  imply having tatoos or other body modifications
\item
  \textbf{Privacy of Behaviour and Action:} Association with churches or
  poltical organizations could imply certain activities.
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Association with churchs of
  political organizations could imply a certain intellectual attitude.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} reflexive violation
\end{itemize}

@@

\section{IT Security}

@@

\subsubsection{threat}

\emph{threat} is a class of potential events whose manifestation can
cause damage or harm.

\subsubsection{vulnerability}

A weakness which can cause the loss of security.

\subsubsection{hazard}

Concrete risk due to one or more concrete vulnerabilities \textbf{AND}
corresponding threats.

@@

\subsubsection{incident}

An event caused by a threat manifestation against one or more
corresponding vulnerabilities.

@@

\subsubsection{accident}

An incident which did cause damage or harm. (Translates to
\emph{Schandensfall/Zwischenfall/Störfall} in german)

\subsubsection{non-accident}

An incident which \textbf{did not} cause any damage or harm.

\subsubsection{measure}

A well defined set of one or more activities which reduce or eliminate
vulnerabilities.

\subsection{IT Security Analysis according to Grimm et. al}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  an \textbf{ontology}, which aims to organize common security
  terminology in a reasonable and practical way
\item
  and a systematic analysis \textbf{procedure} based on that ontology
\end{itemize}

\subsubsection{Ontology}

@@

The ontology is organized in four views:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{World:} Contains all components describing the current state.
\item
  \textbf{Potential:} Contains all components describing both the
  desired and dreaded state.
\item
  \textbf{Plan:} Contains all conceptual components required to develop
  sufficient measures to achieve and secure the desired state
  \textbf{or} to create the dreaded state. The \textbf{Plan} view
  \emph{realizes} the \textbf{Potential} view of the system.
  (\textbf{Note:} this should rather be translated with \emph{Concept})
\item
  \textbf{Event:} Contains all actual operations and events through out
  the production phase. The \textbf{Event} view \emph{instantiates} the
  \textbf{Plan} view of the system.
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Assets:} Things of value to one or more stakeholders. The
  value can be \emph{``hard''} (money, data, etc.) or \emph{``soft''}
  (trust,privacy,etc.).
\item
  \textbf{IT-Systems:} The IT-Systems under study.
\item
  \textbf{Humans:} All identifiable actors of the system under study.
  Many problems arise due to misunderstandings during man-machine
  interaction.
\item
  \textbf{Conflicts of Interests:} Different actors have different
  interests. Those interest can be in conflict. A trival conflict is the
  \emph{Attacker-Attackee}-Conflict: a service provider offers private
  data storage, therefore the provider is interested in having the
  access restricted. An attacker is naturally interested in easy access
  in order captialize the stolen data. However, heavy security
  restriction are also a burden for maintenance staff, as they are
  interested in having an easy life. This kind of conflict can create
  vulnerabilities.
\item
  \textbf{Vulnerabilities:} All indentifiable weaknesses in the current
  system layout.
\item
  \textbf{Interactions:} Assets, IT-Systems, Humans and Vulnerabilites
  are in continous interaction with each other in order to
  \emph{support} the \textbf{Business Objectives}. Those interactionscan
  also \emph{lead to} \textbf{Threats}, i.e.~having unencrypted
  communication with a server. Therefore all interactions which occur in
  the system's outline have to be documented.
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Chances/Risks:} Chances and Risks \emph{affect}
  \textbf{Business Objectives} (and \textbf{Threats}).
\item
  \textbf{Business Objectives:} Chances the system under study. This
  describes the desired state.
\item
  \textbf{Threats:} Risks for business objectives, this can simply be
  the integrety of the IT-System. Threats \emph{target} one or more
  \textbf{Assets} and violate \textbf{Security Requirements}. This
  describes the dreaded state.
\item
  \textbf{Security Requirements:} A set of distinct requirements for a
  safe and secure system. Security requirements \emph{hold for} one or
  more \textbf{Assets}. This describes the potential state after this
  procedure.
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Business Model:} The plan to achieve \textbf{Business
  Objectives}
\item
  \textbf{Accident Scenario:} This is either the plan of a certain
  attack or the concrete outline of random disaster. Although the latter
  is most likely hard to anticipate.
\item
  \textbf{Attack Technique:} A specific technique or technology to
  attack IT-Systems (Man in the Middel, Phishing, etc.). (\textbf{Note:}
  This component is not conform to the glossary as the term
  \emph{accident} there covers both disaster and attack!)
\item
  \textbf{Security Measures:} The plan to achieve a safe and secure
  system. Each \textbf{Security Mesaure} \emph{opposes} an
  \textbf{Accident Scenario} or an \textbf{Attack Technique}.
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Business Process:} The actual, running instance of the
  \textbf{Busieness Modell}
\item
  \textbf{Accidents:} All actually happened accidents.
\item
  \textbf{Attacks:} All actually happened attacks. (\textbf{Note:} This
  component is not conform to the glossary as the term \emph{accident}
  there covers both disaster and attack!)
\item
  \textbf{Security Operations:} Instances of \textbf{Security Measures}.
  Security Measures \emph{secure} the system against \textbf{Accidents}
  and \textbf{Attacks}.
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  all \textbf{Assets} which must be protected
\item
  all relevant \textbf{IT-Systems}
\item
  all involved \textbf{Humans} and their \textbf{Conflicts of Interests}
\item
  all known \textbf{Vulnerabilities}
\item
  and all important \textbf{Interactions} between the former components.
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  a \emph{threat specifiation}, which identifies the \textbf{Threat} and
  its targeted \textbf{Assets}
\item
  a \emph{threat risk evaluation}, which detrmines the likelyhood of a
  threat manifestation
\item
  a \emph{hazard matrix}, which maps threats to known
  \textbf{Vulnerabilities} and identifies potential hazards
\item
  a \emph{security requirement specifiation}, which specifies
  requirments in order to deal with identified hazards
\end{itemize}

@@

%\includegraphics{../diagrams/png/scenario01-ServerSideMining.png}
\input{./figures/LG-Operation-Scenario-01-Server-Side-Mining}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  citizens want to be unidentifiable
\item
  citizens want certain informations about them to be secret
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  staff wants proper payment
\item
  local authorities want to reduce cost
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  citizens want to be unidentifiable
\item
  citizens want certain informations about them to be secret
\item
  criminals want to posses certain information about a citizen
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  criminals want to harm the system
\item
  technical staff has to keep the system safe and sound
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  criminals want to harm the system
\item
  criminals want access to collected data
\item
  local authorities have to keep collected data restricted
\item
  local authorities want a stable system
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Unauthorized access to privacy sensitive data}, caused by
  \begin{itemize}
  \item
    \textbf{Excessive Data Mining} Linking sensor data provided by
    citizens with additional sources can produce more privacy sensitive
    data.
  \item
    \textbf{Corrupt Local Authorities} Local Authorities have certain data
    access, they could hand over this access for monetary reasons.
  \item
    \textbf{Corrupt/Unhappy Staff} Staff members also have a certain data
    access and they also could hand over this access for monetary reasons
    or as a form of payback for unfair treatment.
  \item
    \textbf{Competent Attackers} Competent Attackers are always a threat
    for IT-systems. Normaly they have monetary reasons to exploit a
    system, but there is also a possibility for proof-of-concept like
    attacks.
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Phone Number
\item
  IP Address
\item
  Public-administrative Data (Date of Birth, population register)
\item
  Data held by organizations, like Banks or Insurance Companies
\item
  All data that is stored in online services (Facebook)
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \emph{WHO} collects data?
\item
  \emph{WHAT} data will be collected?
\item
  \emph{WHY} will data be collected and processed?
\item
  \emph{HOW} will data be collected and processed?
\item
  \emph{WHEN} will data expire?
\item
  What is allowed?
\item
  What choices ar possible?
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Comprehension:} access to hard facts
\item
  \textbf{Consistency:} trust that those facts are reliable
\item
  \textbf{Conciousness:} awareness of those facts to found choices
\end{itemize}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Choice}
  \begin{itemize}
  \item
    \textbf{Consent:} the choice to opt-in
  \item
    \textbf{Confinement:} the choice to set limits regarding user data
  \item
    \textbf{Context:} the choice to set limits regarding user data
    depending on certain context
  \end{itemize}

@@

\section{References}

>>>>

\chapter{Legal and Ethical aspects of Privacy}

@@

%\includegraphics{../diagrams/png/implicit-privacy-violation-matrix.png}
\input{./figures/Implicit-Privacy-Violation-Matrix}

\paragraph*{Privacy of The Person}

@@

\item
  \textbf{Privacy of The Person:} reflexive violation
\item
  \textbf{Privacy of Behaviour and Action:} none
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Some psychological diseases
  (e.g.~depression) have physiological impact. Such physiological
  patterns could be detected.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} none
\end{itemize}

\paragraph*{Privacy of Behaviour and Action}

@@

\item
  \textbf{Privacy of The Person:} Religious practices may include body
  modifications (e.g.~circumcision).
\item
  \textbf{Privacy of Behaviour and Action:} reflexive violation
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Social activities in
  general depend on a certain intellectual attitude. Such an actvity is
  the expressions of such an attitude.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} Recording religious, politcal or
  sexual activities can reveal association with churches, political
  parties or sexual partners.
\end{itemize}

\paragraph*{Privacy of Communication}

@@

\item
  \textbf{Privacy of The Person:} Communication about body
  characteristics.
\item
  \textbf{Privacy of Behaviour and Action:} Communicatio about social
  activities.
\item
  \textbf{Privacy of Communication:} reflexive violation
\item
  \textbf{Privacy of Data and Image:} Communication containing one's
  passwords or other sensitive data.
\item
  \textbf{Privacy of Thoughts and Feelings:} Communication of thoughts
  and feelings, e.g.~wiretapping a flirt or a catholic confession
  ritual.
\item
  \textbf{Privacy of Location and Space:} Interception of face-to-face
  communication is only possible if one's location and space is violated
  (wiretapping).
\item
  \textbf{Privacy of Association:} Communication about one's
  associations (family members, churches, etc.).
\end{itemize}

\paragraph*{Privacy of Data and Image}

@@

\item
  \textbf{Privacy of The Person:} Images or stored biometric information
  reveal one's physical characteristics.
\item
  \textbf{Privacy of Behaviour and Action:} Images or diaries can reveal
  one's social activities.
\item
  \textbf{Privacy of Communication:} Modern communication systems
  usually contain some sort of archive function, e.g.~E-mail clients do
  not automatically delete messages. Such messages are data and reveal
  one's communication.
\item
  \textbf{Privacy of Data and Image:} reflexive violation
\item
  \textbf{Privacy of Thoughts and Feelings:} Images can show one's
  emotional state.
\item
  \textbf{Privacy of Location and Space:} Images can reveal one's
  location, e.g.~making a picture in front of the Eifel Tower.
\item
  \textbf{Privacy of Association:} E-mail data can also reveal
  association.
\end{itemize}

\paragraph*{Privacy of Thoughts and Feelings}

@@

\item
  \textbf{Privacy of The Person:} Thoughts and feelings can reveal
  medical conditions.
\item
  \textbf{Privacy of Behaviour and Action:} Thoughts and feelings can
  reveal a certain attitudes which create a foundation for certain
  social activities.
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} reflexive violation
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} Thoughts and feelings can reveal
  individual association, e.g amorous feelings for a certain person.
\end{itemize}

\paragraph*{Privacy of Location and Space}

@@

\item
  \textbf{Privacy of The Person:} Frequently visited doctors can reveal
  certain medical conditions, if such doctors are known specialsts. In
  general it could imply ill-being.
\item
  \textbf{Privacy of Behaviour and Action:} Frequently visited places in
  general can reveal association and hence implies social activities.
\item
  \textbf{Privacy of Communication:} If one's location is knwon, it is
  possible to intercept (wiretap) one's communication. This also may
  violate the right to private spaces.
\item
  \textbf{Privacy of Data and Image:} If one's location is known, it is
  possible shoot pictures. This violates the right to one's image
  (\emph{``Recht am eigenen Bild''}).
\item
  \textbf{Privacy of Thoughts and Feelings:} Frequently visited persons
  may imply certain thoughts and feelings, e.g.~having a mistress.
\item
  \textbf{Privacy of Location and Space:} reflexive violation
\item
  \textbf{Privacy of Association:} Frequently visted places can reveal
  associations simply by searching in maps or yellow-pages.
\end{itemize}

\paragraph*{Privacy of Association}

@@

\item
  \textbf{Privacy of The Person:} Association with tatoo artists could
  imply having tatoos or other body modifications
\item
  \textbf{Privacy of Behaviour and Action:} Association with churches or
  poltical organizations could imply certain activities.
\item
  \textbf{Privacy of Communication:} none
\item
  \textbf{Privacy of Data and Image:} none
\item
  \textbf{Privacy of Thoughts and Feelings:} Association with churchs of
  political organizations could imply a certain intellectual attitude.
\item
  \textbf{Privacy of Location and Space:} none
\item
  \textbf{Privacy of Association:} reflexive violation
\end{itemize}

@@

\pagebreak

\chapter{Privacy Analysis of Live+Gov Systems}

\section{IT Security Analysis according to Grimm et. al}

\item
  a \textbf{model}, which aims to organize common security
  terminology in a reasonable and practical way
\item
  and a systematic analysis \textbf{procedure} based on that ontology
\end{itemize}

@@

\item A \emph{threat} is a class of potential events whose manifestation can
cause damage or harm.

\item A \emph{vulnerability} is a weakness which can cause the loss of security.

\item a \emph{hazard} is a concrete risk due to one or more concrete vulnerabilities and corresponding threats.

@@

\item An \emph{incident} is an event caused by a threat manifestation against one or more
corresponding vulnerabilities.

@@

\item An \emph{accident} is an incident which did cause damage or harm. (Translates to 'Schandensfall/Zwischenfall/Störfall' in the German language).

\item A \emph {non-accident} is an incident which did not cause any damage or harm.

\item A security \emph{measure} is a set of one or more activities which reduce or eliminate
vulnerabilities.

\subsection{Model}

@@

The model is organized in four views:

\item
  \textbf{World:} Contains all components describing the current state.
\item
  \textbf{Potential:} Contains all components describing both the
  desired and dreaded state.
\item
  \textbf{Plan:} Contains all conceptual components required to develop
  sufficient measures to achieve and secure the desired state
  \textbf{or} to create the dreaded state. The \textbf{Plan} view
  \emph{realizes} the \textbf{Potential} view of the system.
  (\textbf{Note:} this should rather be translated with \emph{Concept})
\item
  \textbf{Event:} Contains all actual operations and events through out
  the production phase. The \textbf{Event} view \emph{instantiates} the
  \textbf{Plan} view of the system.
\end{itemize}

@@

\item
  \textbf{Assets:} Things of value to one or more stakeholders. The
  value can be \emph{``hard''} (money, data, etc.) or \emph{``soft''}
  (trust,privacy,etc.).
\item
  \textbf{IT-Systems:} The IT-Systems under study.
\item
  \textbf{Humans:} All identifiable actors of the system under study.
  Many problems arise due to misunderstandings during man-machine
  interaction.
\item
  \textbf{Conflicts of Interests:} Different actors have different
  interests. Those interest can be in conflict. A trival conflict is the
  \emph{Attacker-Attackee}-Conflict: a service provider offers private
  data storage, therefore the provider is interested in having the
  access restricted. An attacker is naturally interested in easy access
  in order captialize the stolen data. However, heavy security
  restriction are also a burden for maintenance staff, as they are
  interested in having an easy life. This kind of conflict can create
  vulnerabilities.
\item
  \textbf{Vulnerabilities:} All indentifiable weaknesses in the current
  system layout.
\item
  \textbf{Interactions:} Assets, IT-Systems, Humans and Vulnerabilites
  are in continous interaction with each other in order to
  \emph{support} the \textbf{Business Objectives}. Those interactionscan
  also \emph{lead to} \textbf{Threats}, i.e.~having unencrypted
  communication with a server. Therefore all interactions which occur in
  the system's outline have to be documented.
\end{itemize}

@@

\item
  \textbf{Chances/Risks:} Chances and Risks \emph{affect}
  \textbf{Business Objectives} (and \textbf{Threats}).
\item
  \textbf{Business Objectives:} Chances the system under study. This
  describes the desired state.
\item
  \textbf{Threats:} Risks for business objectives, this can simply be
  the integrety of the IT-System. Threats \emph{target} one or more
  \textbf{Assets} and violate \textbf{Security Requirements}. This
  describes the dreaded state.
\item
  \textbf{Security Requirements:} A set of distinct requirements for a
  safe and secure system. Security requirements \emph{hold for} one or
  more \textbf{Assets}. This describes the potential state after this
  procedure.
\end{itemize}

@@

\item
  \textbf{Business Model:} The plan to achieve \textbf{Business
  Objectives}
\item
  \textbf{Accident Scenario:} This is either the plan of a certain
  attack or the concrete outline of random disaster. Although the latter
  is most likely hard to anticipate.
\item
  \textbf{Attack Technique:} A specific technique or technology to
  attack IT-Systems (Man in the Middel, Phishing, etc.). (\textbf{Note:}
  This component is not conform to the glossary as the term
  \emph{accident} there covers both disaster and attack!)
\item
  \textbf{Security Measures:} The plan to achieve a safe and secure
  system. Each \textbf{Security Mesaure} \emph{opposes} an
  \textbf{Accident Scenario} or an \textbf{Attack Technique}.
\end{itemize}

@@

\item
  \textbf{Business Process:} The actual, running instance of the
  \textbf{Busieness Modell}
\item
  \textbf{Accidents:} All actually happened accidents.
\item
  \textbf{Attacks:} All actually happened attacks. (\textbf{Note:} This
  component is not conform to the glossary as the term \emph{accident}
  there covers both disaster and attack!)
\item
  \textbf{Security Operations:} Instances of \textbf{Security Measures}.
  Security Measures \emph{secure} the system against \textbf{Accidents}
  and \textbf{Attacks}.
\end{itemize}

@@

\item
  all \textbf{Assets} which must be protected
\item
  all relevant \textbf{IT-Systems}
\item
  all involved \textbf{Humans} and their \textbf{Conflicts of Interests}
\item
  all known \textbf{Vulnerabilities}
\item
  and all important \textbf{Interactions} between the former components.
\end{itemize}

@@

\item
  a \emph{threat specifiation}, which identifies the \textbf{Threat} and
  its targeted \textbf{Assets}
\item
  a \emph{threat risk evaluation}, which detrmines the likelyhood of a
  threat manifestation
\item
  a \emph{hazard matrix}, which maps threats to known
  \textbf{Vulnerabilities} and identifies potential hazards
\item
  a \emph{security requirement specifiation}, which specifies
  requirments in order to deal with identified hazards
\end{itemize}

@@

%\includegraphics{../diagrams/png/scenario01-ServerSideMining.png}
\input{./figures/LG-Operation-Scenario-01-Server-Side-Mining}
\input{./figures/IT-Systems}

@@

@@

\item
  citizens want to be unidentifiable
\item
  citizens want certain informations about them to be secret
\end{itemize}

@@

\item
  staff wants proper payment
\item
  local authorities want to reduce cost
\end{itemize}

@@

\item
  citizens want to be unidentifiable
\item
  citizens want certain informations about them to be secret
\item
  criminals want to posses certain information about a citizen
\end{itemize}

@@

\item
  criminals want to harm the system
\item
  technical staff has to keep the system safe and sound
\end{itemize}

@@

\item
  criminals want to harm the system
\item
  criminals want access to collected data
\item
  local authorities have to keep collected data restricted
\item
  local authorities want a stable system
\end{itemize}

@@

\input{./figures/ThreatTable}

\item
  \textbf{Unauthorized access to privacy sensitive data}, caused by
  \begin{itemize}
  \item
    \textbf{Excessive Data Mining} Linking sensor data provided by
    citizens with additional sources can produce more privacy sensitive
    data.
  \item
    \textbf{Corrupt Local Authorities} Local Authorities have certain data
    access, they could hand over this access for monetary reasons.
  \item
    \textbf{Corrupt/Unhappy Staff} Staff members also have a certain data
    access and they also could hand over this access for monetary reasons
    or as a form of payback for unfair treatment.
  \item
    \textbf{Competent Attackers} Competent Attackers are always a threat
    for IT-systems. Normaly they have monetary reasons to exploit a
    system, but there is also a possibility for proof-of-concept like
    attacks.
  \end{itemize}
\end{itemize}

@@

\item
  Phone Number
\item
  IP Address
\item
  Public-administrative Data (Date of Birth, population register)
\item
  Data held by organizations, like Banks or Insurance Companies
\item
  All data that is stored in online services (Facebook)
\end{itemize}

@@

\item
  \emph{WHO} collects data?
\item
  \emph{WHAT} data will be collected?
\item
  \emph{WHY} will data be collected and processed?
\item
  \emph{HOW} will data be collected and processed?
\item
  \emph{WHEN} will data expire?
\item
  What is allowed?
\item
  What choices ar possible?
\end{itemize}

@@

\item
  \textbf{Comprehension:} access to hard facts
\item
  \textbf{Consistency:} trust that those facts are reliable
\item
  \textbf{Conciousness:} awareness of those facts to found choices
\end{itemize}

@@

\item
  \textbf{Choice}
  \begin{itemize}
  \item
    \textbf{Consent:} the choice to opt-in
  \item
    \textbf{Confinement:} the choice to set limits regarding user data
  \item
    \textbf{Context:} the choice to set limits regarding user data
    depending on certain context
  \end{itemize}

@@

% \section{References}
